---
title: Scatter Plots
author: ''
date: '2017-10-16'
slug: scatter-plots
categories: []
tags: []
---


We first want to take data from the Lahman database, which includes baseball stastics. 
```{r setup, include=(FALSE)} 
library(Lahman)
library(sqldf)
library(ggplot2)
```
Once these libraries are loaded, we need to extract the data that is desired. Let's look at an example.

Find the total career homeruns and strikeouts from players who had more than 400 homeruns. 

```{r}
query<-"SELECT playerID,sum(HR),sum(SO)
FROM Batting
Group BY playerID
HAVING sum(HR)>400"
sqldf(query)
```
Now we must save it as result.
```{r}
query<-"SELECT playerID,sum(HR) AS CareerHR,sum(SO) AS CareerSO
FROM Batting
Group BY playerID
HAVING sum(HR)>400"
result<-sqldf(query)
```
Once we have gathered the data, we must visualize it by creating a scatter plot. This will be done using the following code. 
```{r}
ggplot()+
  geom_point(data=result, aes(x=CareerSO, y=CareerHR), size=3)+
  ggtitle("Career Strikeouts & Homeruns")+
  xlab("Career Strikeouts")+
  ylab("Career Homeruns")
```

